---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

[![Build Status](https://travis-ci.org/vincenzocoia/powers.svg?branch=master)](https://travis-ci.org/vincenzocoia/powers)

__Note__: This R package was developed for a class assignment. It is useful but not maintained. 

# coordinates

This is an R package that allows you to attach values to coordinate points and manipulate them.

## Installation

You can install powers from github with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("")
```

## Example

See the vignette for more extensive use, but here's an example:

```{r example}
powers::reciprocal(2)
```

## For Developers

(Again, I don't actually intend for anyone to develop this silly package, but if I did, here's what I'd write.)

This package offers the great potential to practice code collaboration and package development. If you are interested in contributing, developing a method that automatically pairs equal coordinate points before value manipulation could be extremely helpful. Check out the [`Ops.coords` method]() for further development.
